\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage[colorinlistoftodos]{todonotes}
\pagestyle{empty}

\title{EDAF05 - Assignment 5}
\author{Eric Rostedt \\ Mattias Pettersson}

\begin{document}
\maketitle

\section{Results}

\todo[inline]{Briefly comment the results, did the script say all your solutions were correct? Approximately how long time does it take for the program to run on the largest input? What takes the majority of the time?}
When checking the solution by running ./check\_solution.py we get that the implementation is correct. When running the code on the largest file we get a total running time of about 14.7 seconds and out of that almost all time is spent in constructing the opt (dp in our case) matrix for each query. 

\section{Implementation details}

\todo[inline]{How did you implement the solution? Which data structures were used? Which modifications to these data structures were used? What is the overall running time? Why?}\\
We read the input using the sys.std.readlines function and split it into one tuple of words (words to be matched), and one defaultdict of tuples containing the different letter combinations and their respective values.\\

We then begin by creating the opt matrix by filling the first row and first column with i*sigma, representing the penalty if one string is longer than the other. We then start at (1,1) in the opt-matrix and start iterating over the entire matrix in order to find all the opt-values by checking the value above, to the left, and diagonally (top-left) while adding sigma or the dictionary value to the cost.\\

When we have filled the entire matrix we start at the bottom-right corner and start iterating back up to the top-left corner, with every step finding the lowest cost possible (in the same way that we created the opt matrix in the first place). With every step we add a letter or a "*" to the two strings. In the end we reverse the strings and return them.\\

Total running time: 17 seconds.
\end{document}
